Appendix

### 2019-07-15 manuscript/appendix.Rmd
show trophic state with waffle charts

```{r trophic_state, fig.cap="Lake trophic state", fig.width = 5.5, fig.height = 4, warning=FALSE, message=FALSE}

dt <- readRDS("../data/dt.rds") %>%
  dplyr::filter(!is.na(chla)) %>%
  mutate(trophic_state = cut(chla, 
                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
                             labels = c("oligotrophic", "mesotrophic", 
                                        "eutrophic", "hypereutrophic"))) %>%
  dplyr::select(chla, trophic_state) %>%
  group_by(trophic_state) %>%
  count()

g <- gridExtra::tableGrob(dt, rows = rep("", nrow(dt)))
grid.draw(g)
```

>>>>

```{r trophic_state, fig.cap="Lake trophic state", fig.width = 5.5, fig.height = 4, warning=FALSE, message=FALSE}
lg <- lagosne_load("1.087.1")
focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
                                             c("56", "57", "36", "37", "38")), 
                         stringsAsFactors = FALSE)

dt <- readRDS("../data/dt.rds") %>%
  dplyr::filter(!is.na(chla)) %>%
  mutate(trophic_state = cut(chla, 
                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
                             labels = c("oligotrophic", "mesotrophic", 
                                        "eutrophic", "hypereutrophic"))) %>%
  dplyr::select(chla, trophic_state) %>%
  group_by(trophic_state) %>%
  count() %>%
  ungroup() %>% # rowwise() %>%
  mutate(frac = (n / sum(n)) * 100)

lg_trophic_state <- dplyr::filter(lg$epi_nutr, 
                                  !(lagoslakeid %in%
                                      readRDS("../data/dt.rds")$lagoslakeid)) %>%
  dplyr::filter(!is.na(chla)) %>%
  dplyr::select(chla, lagoslakeid, sampledate) %>%
  group_by(lagoslakeid) %>%
  summarise(chla = median(chla)) %>%
  mutate(trophic_state = cut(chla, 
                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
                             labels = c("oligotrophic", "mesotrophic", 
                                        "eutrophic", "hypereutrophic"))) %>%
  dplyr::select(chla, trophic_state) %>%
  group_by(trophic_state) %>%
  count() %>%
  ungroup() %>% # rowwise() %>%
  mutate(frac = (n / sum(n)) * 100)

dt <- data.frame(`Trophic State` = dt$trophic_state, 
           `Study` = round(dt$frac, 1), 
           `All` = round(lg_trophic_state$frac, 1), 
           stringsAsFactors = FALSE)
dt <- setNames(dt, c("Trophic State", "This Study", "All Lakes"))

# g <- gridExtra::tableGrob(dt, rows = rep("", nrow(dt)))
# grid.draw(g)

# waffle
library(waffle)
library(hrbrthemes)

ggplot(tidyr::gather(dt, key = "key", value = "value", -`Trophic State`),
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=1.125, n_rows = 7) +
  facet_wrap(~key, ncol=1) +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0)) +
  ggthemes::scale_fill_tableau(name=NULL) +
  coord_equal() +
  labs(title = "Trophic State")  +
#   theme_ipsum_rc(grid="") +
   theme_enhance_waffle() + 
  theme(strip.background = element_blank())

# highlighted regions
test <- readRDS("../data/dt.rds") %>%
  mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>%
  dplyr::filter(!is.na(chla)) %>%
  mutate(trophic_state = cut(chla, 
                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
                             labels = c("oligotrophic", "mesotrophic", 
                                        "eutrophic", "hypereutrophic"))) %>%
  dplyr::select(lagoslakeid, is_focal, chla, hu4_zoneid, trophic_state) %>%
  group_by(is_focal, trophic_state) %>%
  count() %>%
  tidyr::spread(trophic_state, n)
```

```{r predictor_maps}
# 
```
